Psyc 601 Multivariate Statistics Project

### 2013-08-26 writeups/proposal/proposal.tex
foo
Former-commit-id: 6a45608d5941ef028562fe183477862d16283368 [formerly 4ed51fc7eb51ff77dd9ea92c926726bf48ec4ae5]
Former-commit-id: 9e21fbe337271d5b5146cd11ebecb7254040ddd2

This tweet-centered approach is quite different than the hashtag-centered approach presented in \textcite{Mazzia2009}.
With a hashtag-centered approach, a direct association is built between the words in a tweet and hashtags that occur in tweets.
With a tweet-centered approach, that association between words and hashtags is indirect:
The relationship is built between words in a tweet and a user, and then similar users are assumed to use similar hashtags.
One problem with the tweet-centered approach is that the storage size grows with the number of tweets, as a vector representatino of the content in each tweet has to be maintained to later compute tweet similarity.
The storage size for a hashtag-centered approach grows with the number of hashtags, but it seems reasonable that this will grow slower than the number of tweets and asymptote after collecting a large sample of tweets.
So from the perspective of efficient information storage and retrieval, it seems more likely that the hashtag-centered approach used in \textcite{Mazzia2009} will scale as Twitter grows in size and use.

>>>>

This tweet-centered approach is quite different than the hashtag-centered approach presented in \textcite{Mazzia2009}.
With a hashtag-centered approach, a direct association is built between the words in a tweet and hashtags that occur in tweets.
With a tweet-centered approach, that association between words and hashtags is indirect:
The relationship is built between a tweet and its content, and then similar tweets are assumed to use similar hashtags.
One problem with the tweet-centered approach is that the storage size grows with the number of tweets, as a vector representatino of the content in each tweet has to be maintained to later compute tweet similarity.
The storage size for a hashtag-centered approach grows with the number of hashtags, but it seems reasonable that this will grow slower than the number of tweets and asymptote after collecting a large sample of tweets.
So from the perspective of efficient information storage and retrieval, it seems more likely that the hashtag-centered approach used in \textcite{Mazzia2009} will scale as Twitter grows in size and use.
